Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-07-01 paper/paper.tex
integrate conversation with David Smith

Consequently, the PMC may contribute to overall DMN function
by monitoring the subjective outcomes
of possible actions and integrating that information
with memory and perspective frames
into short- and longer-term behavioral agendas.
Estimated value, that differs across individuals, probably enriches
statistical assessment of the environment
to map and predict delayed reward opportunities in the future.
In doing so, the PMC may continuously adapt the organism to changes
in both the external environment and its internal representation
to enable strategic behavior.

@@

The dmPFC may subserve inference, representation, and assessment
of one's own and other individuals' action considerations.
Generally,
neurological patients with tissue damage in the prefrontal cortex
are known to struggle with
adaptation to new stimuli and events
\citep{stuss1986frontal}.
Specifically, neural activity in the human dmPFC
reflected expectations about other peoples' actions and
outcomes of these predictions.
Neural activity in the dmPFC indeed explained the performance decline
of inferring other peoples' thoughts in aging humans \citep{moran2012social}.
Certain dmPFC neurons in macaque monkeys exhibited a preference
for processing others', rather than own, behavior
with fine-grained adjustment of contextual circumstances \citep{yoshida2010neural}.
% In fact, the spatially neighboring dorsal anterior cingulate cortex
% has also been linked to computing values and efforts of
% persisting a behavioral plan versus switching the
% environmental context in several lesion studies \citep{kolling2016value}.
%
Such highly abstract neural computations necessarily rely on the
construction of probabilistic internal information drawing from
memory recall, mental scene elaboration processes,
and stored knowledge of world regularities.
\begin{wrapfigure}{r}{.4\linewidth}
  \includegraphics[width=1.\linewidth]{fig_dmn.png}
  \centering
  \caption{\textbf{Morphological coupling between reward system and
  default mode network.} Based on 9,932 human subjects from the UK Biobank, inter-individual differences in left NAc volume ($R^2=0.11 \pm 0.02$) and right NAc volume ($R^2=0.14 \pm 0.02$) could be predicted from volume in the DMN nodes. These out-of-sample generalization performances were obtained from support vector regression applied to normalized node volumes in the DMN in a 10-fold cross-validation procedure. 
  Consistent for the left and right reward system, NAc volume in a given subject is
  positively coupled with the vmPFC and HC.
  Code and data for reproduction and visualization:
  \url{www.github.com/banilo/to_be_added_later}.
  }
  \label{fig:dmn}
\end{wrapfigure}
%
Moreover,
in a computational neuroimaging experiment,
dorsomedial PFC activity preferentially processed the consequences of
action choices that were considered but not actually executed,
whereas ventromedial PFC (vmPFC) activity
processed especially value outcomes of actions actually performed on the environment
\citep{nicolle2012agent}.

>>>>

Consequently, the PMC may contribute to overall DMN function by
``altering behavior in response to unexpected change''
\citep{pearson2011posterior}.
This DMN node probably
monitors sudden and gradual environmental changes in subjective outcomes
of action choices for integration
with memory and perspective frames
to improve short- and longer-term behavioral agendas.
Estimated value, that differs across individuals, probably enriches
statistical assessment of the environment
to map and predict delayed reward opportunities in the future.
In doing so, the PMC may continuously adapt the organism to changes
in both the external environment and its internal representation
to enable strategic behavior.

@@

The dmPFC may subserve inference, representation, and assessment
of one's own and other individuals' action considerations.
Generally,
neurological patients with tissue damage in the prefrontal cortex
are known to struggle with
adaptation to new stimuli and events
\citep{stuss1986frontal}.
Specifically, neural activity in the human dmPFC
reflected expectations about other peoples' actions and
outcomes of these predictions.
Neural activity in the dmPFC indeed explained the performance decline
of inferring other peoples' thoughts in aging humans \citep{moran2012social}.
Certain dmPFC neurons in macaque monkeys exhibited a preference
for processing others', rather than own, behavior
with fine-grained adjustment of contextual circumstances \citep{yoshida2010neural}.
% In fact, the spatially neighboring dorsal anterior cingulate cortex
% has also been linked to computing values and efforts of
% persisting a behavioral plan versus switching the
% environmental context in several lesion studies \citep{kolling2016value}.
%
Such highly abstract neural computations necessarily rely on the
construction of probabilistic internal information drawing from
memory recall, mental scene elaboration processes,
and stored knowledge of world regularities.
\begin{wrapfigure}{r}{.4\linewidth}
  \includegraphics[width=1.\linewidth]{fig_dmn.png}
  \centering
  \caption{\textbf{Morphological coupling between reward system and
  default mode network.} Based on 9,932 human subjects from the UK Biobank, inter-individual differences in left NAc volume ($R^2=0.11+/-0.02$) and right NAc volume ($R^2=0.14+/-0.02$) could be predicted from volume in the DMN nodes. These out-of-sample generalization performances were obtained from support vector regression applied to normalized node volumes in the DMN in a 10-fold cross-validation procedure. 
  Consistent for the left and right reward system, NAc volume in a given subject is
  positively coupled with the vmPFC and HC.
  Code and data for reproduction and visualization:
  \url{www.github.com/banilo/to_be_added_later}.
  }
  \label{fig:dmn}
\end{wrapfigure}
%
Moreover,
in a computational neuroimaging experiment,
dorsomedial PFC activity preferentially processed the consequences of
action choices that were considered but not actually executed,
whereas ventromedial PFC (vmPFC) activity
processed especially value outcomes of actions actually performed on the environment
\citep{nicolle2012agent}.
